---
title: 'Critique of Laufenberg Paper'
subtitle: 'Stat 512: Final Project'
author: "Steve Huysman & Parker Levinson"
date: "Friday, April 14, 2023"
output:
  bookdown::pdf_document2: default
  html_document:
    df_print: paged
fontsize: 12pt
header-includes:
- \usepackage{setspace}
- \usepackage{amsmath}
indent: yes

---
```{r setup, eval=TRUE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, eval = TRUE, include = FALSE}
# load packages
library(faraway)
library(tidyverse)
library(catstats)
library(MuMIn)
library(GGally)
library(dplyr)
```


\doublespacing

## Introduction
Introduction (20 pts: rubric × 2)
• Brief overview of the general research area and problem stated (2 pages max)
• Question(s) of interest clearly stated and described, and are specific to what can be
addressed with a statistical analysis. Description of simplification to the authors’
research question and model, if necessary
• Everything stated in the context of the research

## Methods

### Field Methods/Study design 
### Statistical Procedures Used

## Results/Summary of Statistical Findings

## Scope of Inference

## Critique

## Group Work Statement

## References

## Appendix
